Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-09-06 paper/main.tex
more writing
some minor changes to simplify the code

\title{Mallows, Black-box combinatorial optimization, limited budget,  ???}
\author{Ekhiñe Irurozki\inst{1} \and Manuel López-Ibáñez\inst{2}\orcidID{0000-0001-9974-1295}}
\institute{
   Basque Center for Applied Mathematics\\
   \email{eirurozki@bcamath.org}
   \and
   University of Málaga, Málaga, Spain\\
   \email{manuel.lopez-ibanez@uma.es}
}
\date{}%

@@

\begin{abstract}
%The abstract should briefly summarize the contents of the paper in
%150--250 words.
  Black-box combinatorial optimization problems arise in practice when the
  objective function is evaluated by means of a simulator or a real-world
  experiment. In such cases, classical techniques such as mixed-integer
  programming and local search cannot be applied. Moreover, often each solution
  evaluation is expensive in terms of time or resources, thus only a limited
  number of evaluations is possible, typically several order of magnitude
  smaller than in white-box optimization problems. In the continuous case,
  Bayesian optimization, in particular using Gaussian processes, has proven
  very effective under these conditions. Much less research is available in the
  combinatorial case. In this paper, we propose and analyze an
  estimation-of-distribution (EDA) algorithm based on a Mallows probabilistic
  model and compare it with CEGO, a Bayesian optimization algorithm for
  combinatorial optimization. Experimental results show that the Bayesian
  algorithm is able to obtain very good solutions with very few evaluations,
  however, at a significant computational cost, whereas the proposed EDA
  outperforms CEGO when the number of solutions evaluated approaches 400, and
  it is significantly faster. These results suggest that the combination of
  Bayesian optimization and a Mallows-based EDA may be an interesting direction
  for future research.

\keywords{Combinatorial optimization \and Bayesian optimization \and Expensive black-box optimization \and Estimation of distribution algorithms}
\end{abstract}

@@

We use the implementation of GECO provided by the
authors\footnote{\url{https://cran.r-project.org/package=CEGO}}. Following the authors of CEGO~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, we use and the GA that optimizes
the surrogate models uses a population size of 20, crossover rate of 0.5,
mutation rate of 1, tournament selection of size 2 and probability of 0.9,
interchange mutation (i.e., exchanging two randomly selected elements of the
permutation) and cycle crossover for permutations. The budget of each run of
the GA is \textcolor{red}{$10^4$} evaluations using the
surrogate-model. Although it is never stated in the original paper, the
implementation of CEGO generates a set of initial solutions of size \minit by
means of a max-min-distance sequential design: new solutions are added to the
set sequentially by maximizing the minimum distance to solutions already in the
set. These initial solutions are then evaluated on the actual objective
function and the result is used to build the initial surrogate model.  Here we
use $\minit=20$.\MANUEL{\citet{ZaeStoBar2014:ppsn} uses 10 so we may want to change this}

>>>>

\title{Mallows, Black-box combinatorial optimization, limited budget,  ???}
% Double-blind
\author{Double-blind}
% \author{Ekhiñe Irurozki\inst{1} \and Manuel López-Ibáñez\inst{2}\orcidID{0000-0001-9974-1295}}
% \institute{
%    Basque Center for Applied Mathematics\\
%    \email{eirurozki@bcamath.org}
%    \and
%    University of Málaga, Málaga, Spain\\
%    \email{manuel.lopez-ibanez@uma.es}
% }
\date{}%

@@

\begin{abstract}
%The abstract should briefly summarize the contents of the paper in
%150--250 words.
  Black-box combinatorial optimization problems arise in practice when the
  objective function is evaluated by means of a simulator or a real-world
  experiment. In such cases, classical techniques such as mixed-integer
  programming and local search cannot be applied. Moreover, often each solution
  evaluation is expensive in terms of time or resources, thus only a limited
  number of evaluations is possible, typically several order of magnitude
  smaller than in white-box optimization problems. In the continuous case,
  Bayesian optimization, in particular using Gaussian processes, has proven
  very effective under these conditions. Much less research is available in the
  combinatorial case. In this paper, we propose and analyze an
  estimation-of-distribution (EDA) algorithm based on a Mallows probabilistic
  model and compare it with CEGO, a Bayesian optimization algorithm for
  combinatorial optimization. Experimental results show that the Bayesian
  algorithm is able to obtain very good solutions with very few evaluations,
  however, at a significant computational cost, whereas the proposed EDA
  outperforms CEGO when the number of solutions evaluated approaches 400, and
  it is significantly faster. These results suggest that the combination of
  Bayesian optimization and a Mallows-based EDA may be an interesting direction
  for future research.
\textcolor{red}{16 pages max, deadline: 1 November 2020}
\keywords{Combinatorial optimization \and Bayesian optimization \and Expensive black-box optimization \and Estimation of distribution algorithms}
\end{abstract}

@@

We use the implementation of GECO provided by the
authors\footnote{\url{https://cran.r-project.org/package=CEGO}}. Following the
authors of CEGO~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, we use and
the GA that optimizes the surrogate models uses a population size of 20,
crossover rate of 0.5, mutation rate of 1, tournament selection of size 2 and
probability of 0.9, interchange mutation (i.e., exchanging two randomly
selected elements of the permutation) and cycle crossover for permutations. The
budget of each run of the GA is \textcolor{red}{$10^4$} evaluations using the
surrogate-model. Although it is never stated in the original paper, the
implementation of CEGO generates a set of initial solutions of size
$\minit=10$ by means of a max-min-distance sequential design: new solutions
are added to the set sequentially by maximizing the minimum distance to
solutions already in the set. These initial solutions are then evaluated on the
actual objective function and the result is used to build the initial surrogate
model.% \citet{ZaeStoBar2014:ppsn} uses 10
